sem

### 2023-02-09 scripts/workshop/sem.Rmd
add some text

* Try to incorporate nonlinear regression into model for temperature relationships
  + I want to use a GAM with a smooth term for temperature
* Check to see if there is a problem without having the directed separation test
  + Still not sure why it says there are no independence claims present when it seems like there is?
  + There seems to be a significant relationship between log10(size) ~ cc that isn't being specified but is showing up under the independence claims result

>>>>

* Try to incorporate nonlinear regression into model for temperature relationships
  + I want to use a GAM with a smooth term for temperature - DONE
  + I just had to use the development version of piecewiseSEM
* Check to see if there is a problem without having the directed separation test
  + Still not sure why it says there are no independence claims present when it seems like there is?
  + There seems to be a significant relationship between log10(size) ~ cc that isn't being specified but is showing up under the independence claims result
* Currently we are running all our models with siteXmonth-level data but should we run these models with individual-level data?
  + i.e. the qPCR results?
